Lab 2 Draft Report: COVID-19 Case Rate vs Population and Policy

### 2020-11-18 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Updated title and authors and changed name for submission

---
title: "Draft Report"
author: "203 Section 6, Team 1"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

>>>>

---
title: "Lab 2 Draft Report: COVID-19 Case Rate vs Population and Policy"
author: "Aidan Jackson, Frank Liu, Sam Temlock, Haoyu Zhang"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
